A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-22 text/introduction.tex
Rewrite Sections 1 and 2.
Add MetaOCaml/

\section{Introduction}

@@

Multi-stage programming makes it easier for programmers to implement
generation and execution of code at run time by providing language
constructs for composing and running pieces of code as first-class
values.  A promising application of multi-stage programming is
(run-time) code specialization, which is to generate program code
specialized to partial inputs to the program and such applications are
studied in the literature~\cite{taha2007gentle}  \AI{We should list
applications of multi-stage programming, not necessarily of MetaOCaml.}

>>>>

\section{Introduction}
\label{sec:intro}

@@

Multi-stage programming makes it easier for programmers to implement
generation and execution of code at run time by providing language
constructs for composing and running pieces of code as first-class
values.  A promising application of multi-stage programming is
(run-time) code specialization, which is to generate program code
specialized to partial inputs to the program and such applications are
studied in the literature~\cite{8384206,taha2007gentle}  \AI{We should list
applications of multi-stage programming, not necessarily of MetaOCaml.}
